Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-29 wearables_survey.tex
un-roughed almost all the results

People consider most things to be non-risky.

Self-reportedly, people are concerned about privacy.

\subsection{Data Type}
(REDO) Okay, I list all of the top 10/bottom 10 lists I generated: the one for all recipients, one only with respect to friends, work, and public, and another for the app only. I think the interesting thing to do is to show the shared vs app only lists, and to highight what is different. If I could show the whole list of 70+ for both, that would be most insightful, but I don't have the place for it in this paper, so this will have to do. Maybe I can do a top/bottom 15 at the least, maybe that will be better?

@@

For shared only \\[-.8cm]

@@

For appserver only  \\[-.8cm]

@@

Results were that in the top 10, both app only and shared had: bank info, SSN, PIN, embarrassing photo, naked photo, naked video. Write a sentence on why I think that is here. The differences were that the app had: door pw, sex freq, embarrassing videos, and photos at home, while the shared had the differing top 5 to be work conversations, credit card, username and password,  and phone conversations. It's cool to see that it's like one is talking to a machine or a company and the other to a person, right?

In the low 10, the common 6 were exercise details, age, tv shows, gender, heart rate, and language. For the 4 different low 10, the app only had: phone use, how much you like people, when and what you ate, and eye patterns for tracking. For shared, these 4 were name, having fun or happy, music, and if a person was busy or interruptible. Also, this is interesting. People don't want to share phone use, opinions on people, food habits, or eye patterns, but would find it useful to have for apps, and well, people don't care about observable things or happy/music with people. But maybe not apps since it seems creepy or will give them ads.

\subsection{Data Recipient}
(REDO) Data recipient matters in how upset people get, or well, how much their privacy is invaded and even how secure their information is. What really matters is if it is shared to people or not. There isn't much difference between the friends, work, and public--they are all quite upsetting. Friends is a little lower, but not too significantly (do stats-y thing here). The difference between public being lower than work is probably due to the fact that people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared. Basically, what matters is that there are guarantees that the information is bounded and used in a way that people would assume it would be used.

@@

\subsection{Device Type}
(REDO) So, there is a difference between the device types, but I need to do more work to see if this is statistically significant or not. In either case, this matters the least, and device type and data recipient are more influencing factors. This is just the result of biases in people we can't quite quantify.

@@

with upset rates (cubetastic upset rate | smartphone upset rate)\\
Q1: (14.81\% | 6.13\%)\\
Q2: (44.11\% | 19.85\%)\\
Q3: (87.09\% | 58.44\%)\\
Q4: (52.77\% | 55.79\%)\\
Q5: (86.49\% | 91.82\%)

@@

\subsection{Risk and Benefit Ranks}

We asked users to rate how beneficial or risky a technology was, for all parties affected by the technology (including manufacturers, consumers, and bystanders), over a long period of time, with respect to other, well studied technologies. This gives us an interesting insight into how people perceive these new technologies. For instance, the capacity for facial detection on a wearable device is perceived to be as risky as interacting with a physical lawnmower.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{techplot.png}
	\caption{(This is a placeholder! TODO: generate a better plot; take out the specific wearables too.)}
\end{figure}

(REDO) Talk through the graph shown above. The basic takeaway is that all of the new technologies and capabilities are perceived to be low risk low benefit. We can see that for technologies that people are more familiar with, people rate it more beneficial and more risky (or is it because they are more relevant that they are more familiar to them? Can I make such a claim?). Interesting to note facial recognition versus detection, location tracking, and discrete camera. Refer to appendix \ref{sec:techrank} for the details (if I have space to include such a thing as the absolute benefit and risk ranking and quartiles in this paper..).

\subsection{Perceived Concerns for Wearable Devices}
Near the end of the survey, we asked the participants an open-ended question, asking for the most likely risks associated with owning and interacting with wearable devices. Without any doubt, the answers reaffirm that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}:

@@

Other significant secondary concerns included information compromise (Security), long-term health effects caused from wearing the device (Health), safety hazards from wearing the device, such as battery burns or distractions causing car accidents (Safety), and changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact). Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.

>>>>

Participants assessed many of the new technologies similarly as low risk and low benefit, which we suspect is due to the fact that most are not consciously aware of the way these technologies are being used. Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.

\subsection{Data Type}
To determine the most concerning and least concerning data types, we consider the very upset rate (VUR) of various scenarios. To calculate these rates, we take the rate of responses where participants had indicated that they would be ``very upset'' (the maximum rating) with respect to the total number of responses for the question. Since people considered different things more or less sensitive with respect to the data recipient, we present the most and least concerning shared data along with the most and least concerning ``not shared'' data:

@@

For shared data (friends, work, public) \\[-.8cm]

@@

For not shared data (appserver only)  \\[-.8cm]

@@

Commonly, bank info, SSN, PIN, embarrassing photo, naked photo, naked video were considered to be highly sensitive. When people perceived that the data would be shared with the app only, the other top five concerns included the passcode to a door, how frequently one has sex, embarrassing videos, and photos at home. When people perceived that the data would be shared with a human audience, their other top concerns were work conversations, credit card information, username and password combinations for websites, and phone conversations. When data is perceived to be shared by an app, people are more concerned with issues of being spied on or tracked, whereas when data is perceived to be shared with an individual, people are concerned more with theft or reputation.

On the other hand, exercise details, age, tv shows, gender, heart rate, and language were commonly considered to be lease concerning. When people perceived that the data would be shared with the app only, the other indifferent data included phone use, how much one liked the people around, when and what you ate, and eye patterns. When people perceived that the data would be shared with a human audience, the least concerning data included one's name, if one was having fun, music on the device, and if one was busy or interruptible. When sharing with an application, information otherwise considered personal such as phone use, opinions of people, food eaten, or eye patterns were okay to share, since these seem like useful information to improve one's device experience. However, people are not likely to share the same with people, but are more comfortable with sharing data about topics which would come up in causal conversation.

\subsection{Data Recipient}
People are upset when their data is shared without their permission, regardless of who the recipient is. Generally, there isn't a statistically significant difference between how upset people would be if data were to be shared with friends, work, and public, although when considering each scenario, there are certain scenarios which are considered to be more sensitive with one recipient than another.

Out of all the recipients, friends are considered to be the least upsetting audience, but not too significantly (do stats-y thing here). There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.

@@

\subsection{Device Type}
%For the between-subjects comparison (i.e., participants who received one question, but not the other), you can do either a chi-square test or Fisher's exact test. Both use a 2 x 2 contingency matrix (i.e., rows are outcomes---upset or not---and columns are conditions---wearable or smartphone). The way to choose between the two tests is based on sample size, generally you use chi-square when there are more than 10-20 samples per cell in the table, but using either is just as valid. (A chi-square test can also accommodate more than 2 outcomes, whereas Fisher's exact test only works for 2 x 2; 2 outcomes and 2 conditions). http://en.wikipedia.org/wiki/Fisher%27s_exact_test
%
%For the within-subjects comparisons (i.e., participants received both questions), you would do McNemar's test; which is the within-subjects version of the chi-square test: http://en.wikipedia.org/wiki/McNemar%27s_test
%
%This site is good for quickly doing these tests on summary data: http://graphpad.com/quickcalcs/

(REDO) So, there is a difference between the device types, but I need to do more work to see if this is statistically significant or not. In either case, this matters the least, and device type and data recipient are more influencing factors. This is just the result of biases in people we can't quite quantify.

@@

  (cubetastic upset rate | smartphone upset rate)\\
Q1: (14.81\% | 6.13\%)\\
Q2: (44.11\% | 19.85\%)\\
Q3: (87.09\% | 58.44\%)\\
Q4: (52.77\% | 55.79\%)\\
Q5: (86.49\% | 91.82\%)

@@

\subsection{Risk and Benefit Ranks} 
When assessing new technologies, participants generally had rated the technologies similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}). We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today. A list of the ranking of most risky and most beneficial technologies can be see in appendix \ref{sec:techrank}; the most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).

%should I just put the list in here, in the main part of the paper?

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{techplot.png}
	\caption{(This is a placeholder! TODO: generate a better plot; take out the specific wearables too.)}
	\label{fig:techplot}
\end{figure}

Notably, technologies perceived to be beneficial include location tracking and heart rate detection. Again, this is probably do to the exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device. Technologies considered to be risky, such as a discrete camera and facial detection, seemed to be based on media exposure or general aversion to privacy invasion. However, people are becoming increasingly aware of such risks and are comparing these risks of privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower. As a takeaway, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.

\subsection{Perceived Concerns for Wearable Devices}
Near the end of the survey, we asked the participants an open-ended question regarding the most likely risks associated with owning and interacting with wearable devices. Without any doubt, the answers reaffirm that the most common concern for owning and interacting with wearable devices for the average user is the \textit{possible loss of privacy}:

@@

Other significant secondary concerns included information compromise (Security), financial cost of buying, replacing, or caring for the device (Financial), long-term health effects caused from wearing the device (Health), safety hazards from wearing the device, such as battery burns or distractions causing car accidents (Safety), and changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact). Refer people to the appendix \ref{sec:coding} for detailed information on coding labels.
